---
title: "p8105_hw5_raj2152"
author: "Rachelle Juan"
date: "11/20/2021"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Importing and cleaning the data from _The Washington Post_
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved), 
    n = baltimore_summary %>% pull(n)
    )

baltimore_test %>% 
  broom::tidy()
```


Let's try to iterate across cities.

First, write a function and test it on a few sample cities.

```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved), 
      n = city_summary %>% pull(n)
      )
  
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities.

```{r}
results_df =
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Plot estimates and confidence intervals:

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Alternative solution:
```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2

Start with a dataframe containing all file names using `list.files` function
```{r}
all_file_names =
  tibble(
  files = list.files("./data/zip_data/")
  )
```

Iterate over file names and read in data for each subject using `purrr::map` and saving the result as a new variable in the dataframe
```{r, results = 'hide'}
import_function = function(file_name){
  
  csv_path = str_c("./data/zip_data/", file_name)
  
  read_csv(csv_path)
}
```

Iterate across all files
```{r, message = FALSE}
all_data_df =
  all_file_names %>% 
  mutate(
    results = map(files, import_function)
  ) %>% 
  unnest(results)
```

Tidy the data
```{r}
tidy_data =
  all_data_df %>% 
  separate(files, into = c("arm", "subject_id", sep = 3)) %>% 
  select(-3) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "results"
  ) %>% 
  mutate(
    subject_id = as.numeric(subject_id),
    subject_id_new = ifelse(arm == "exp", subject_id + 10, subject_id)
  )
```

Make a spaghetti plot
```{r}
spaghetti_plot = 
  tidy_data %>% 
  ggplot(aes(x = week, y = results, group = subject_id_new, color = arm)) +
  geom_line() +
  scale_color_brewer(palette = "Set1") 

spaghetti_plot
```

The results of subjects in the experimental group appear to increase over the weeks, while the results of subjects in the control group do not show any observable trends. The results of the experimental group also appear to be higher than the control group.  


## Problem 3

Load the `iris` dataset.
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

Write a function:
```{r}
fill_in_missing = function(vector) {
  
  if (is.numeric(vector)) {
    vector = ifelse(is.na(vector), mean(vector, na.rm = TRUE), vector)
  }
  
  if (is.character(vector)) {
    vector = ifelse(is.na(vector), "virginica", vector)
  }
  return(vector)
}
```

Map across columns and apply function to each column, display some of the new dataframe:
```{r, warning = FALSE}
iris_without_missing =
  map_df(iris_with_missing, fill_in_missing) %>% 
  as.tibble()

iris_without_missing %>% head(25)
```
